---
title: "set up git and github"
author: "Christof Neumann"
date: "2025-02-28"
format: 
  revealjs:
    theme: serif
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# install git and connecting to github

## Mac

- in the console/terminal 

```{bash}
#| eval: false
#| echo: true
#| warning: false
#| error: false
xcode-select --install
```


## Windows


- install Git Bash from https://gitforwindows.org

- install below `C:/Program Files` 

- when asked about "Adjusting your PATH environment", select "Git from the command line and also from 3rd-party software"

- accept the defaults for everything else


## Linux

- I assume you know what you are doing

- if not:


```{bash}
#| eval: false
#| echo: true
#| warning: false
#| error: false
# Ubuntu / Debian Linux:
sudo apt-get install git

# Fedora / RedHat Linux:
sudo yum install git
```


# connect

## access token

- go to R:

```{r, eval = FALSE}
usethis::create_github_token(description = "this is for trying out GitHub")
```

- browser opens, leave the settings (30 day expiration)

- click "Generate Token" at the bottom

- now copy the token into the clipboard and paste to a temporary place where you can retrieve it

- it looks something like `ghp_RFf45gW5gxxxxxxxxxxx`

- this is a PAT (personal access token)


## connect for real

- back to R

```{r, eval = FALSE}
gitcreds::gitcreds_set()
```

- when asked, paste your PAT here

- (if you have an active set of credentials, you may want to keep working with it or delete it)

- you should see something like

```{r}
#| eval: false
-> Adding new credentials...
-> Removing credentials from cache...
-> Done.
```


## let's check


```{r}
#| eval: false
usethis::git_sitrep(tool = "github", scope = "user")
```


- if this shows: `Personal access token for "https://github.com": <discovered>` we are good to go


- if this shows: `Personal access token for "https://github.com": <unset>` we have to try again

  - or get in touch with me



